\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-09 Thesis.tex
done with 1,2,3

Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter. When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations to add information or to show what kind of a relation it is. In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate. Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}). These structural primitives and semantic primitives provide the basics that graphs can be built on.\\

@@

These relations or connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another. As such the temporal associations show the path that a normal lecture would take. The dependencies that are visualized around each frame allow for additional interactiveness.\\

@@

In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge. For Annie this means that she would be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected (see figure \ref{fig:Annie-guided}). It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.\\

@@

For the implementation of \sys, we chose to use impress.js, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations. The open-source presentation framework \textbf{impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka's. It combines HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers. The presentation data is entered in the html file; each slide in its own div with \texttt{data-x}, \texttt{data-y}, and \texttt{data-z} attributes to change the position of the slide. The \texttt{data-x} and \texttt{data-y} axis change the position of the element according to the normal x- and y-axes. The \texttt{data-z} attribute changes the closeness of the elements along the z-axis.\\
\definecolor{bg}{rgb}{0.90,0.90,0.90}

@@

\subsection{The Relational Presentations}
\label{sec:RelationalPresentations}
\ednote{needs work}

>>>>

Visual and normal tree-like graph language have different primitives and it is interesting how the primitives of the former can be mapped to the primitives of the latter. When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations to add information or to show what kind of a relation it is. In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts as a predicate. Thus we can, for instance, express that the Pythagorean theorem depends on information about right angles (similar to \autoref{fig:deppyg}). These structural primitives and semantic primitives provide the basics that graphs can be built on.\\

@@

These relations or connections between different slides do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another. As such the temporal associations show the path that a traditional lecture would take. The dependencies that are visualized around each slide, mainly above or below the slide, allow for additional interactiveness.\\

@@

\begin{wrapfigure}{r}{0.5\textwidth}
\vspace{-24pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.48 \textwidth]{assets/final/arrowsPyth}
    }
  \end{center}
\vspace{-20pt}
  \caption{Connection of Slide}
  \label{fig:arrowspyg}
\vspace{-10pt}
\end{wrapfigure}

In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge. For Annie this means that she will be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected (see figure \ref{fig:arrowspyg}). It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.\\

@@

For the implementation of \sys, impress.js will be used, as commercial applications like Prezi, while more mature in presentations for the general crowd, do not provide us with an Application Programming Interface (API) that allows the generation of whole presentations. The open-source presentation framework \textbf{impress.js} \cite{JSImpress:npentrel14} was created by Bartek Szopka's. It combines HTML and CSS3 which makes it highly customizable but unfortunately renders it unsupported by older browsers. The presentation data is entered in the html file; each slide in its own div with \texttt{data-x}, \texttt{data-y}, and \texttt{data-z} attributes to change the position of the slide. The \texttt{data-x} and \texttt{data-y} axis change the position of the element according to the normal x- and y-axes. The \texttt{data-z} attribute changes the closeness of the elements along the z-axis.\\
\definecolor{bg}{rgb}{0.90,0.90,0.90}

@@

\subsection{The Relational Presentations}
\label{sec:RelationalPresentations}
\ednote{needs work}
\ednote{refer back to primitives: However, the relations can be much more expressive within impress.js.}
